---
title: "TASK 2 - Predict the Optimum number of cluster and represent it visually"
subtitle: "Predict the Optimum number of cluster and represent it visually"
author: "B. Yeshaswini"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=TRUE}
library(datasets) #for using iris data sets load the datasets library.

data("iris")
```

**Iris** dataset gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica.

#### To inspect dataset:

Check the upper value of datasets:
```{r echo=TRUE}
head(iris)
```

To read the total number of rows and columns of iris datasets:
```{r echo=TRUE}
dim(iris)
```

So, the iris datasets have **150 Rows** and **5 Columns**.

To check the details of iris datasets:
```{r echo=TRUE}
summary(iris)
```

### Set Seeds
it ensures that you get the same result if you start with that same seed each time you run the same process.

I set seed to our visualization.
```{r echo=TRUE}
set.seed(8593)
```


## K-Meand Mode:

Now I am removing the species and then assigning them to to variable iris_data, which is makes this process safer and easier.

Because K-Means is applied on non-categorical data.

```{r echo=TRUE}
iris_data <- iris[1:4]
head(iris_data)
```

### find Optimum Cluster or determine the value of k

Mine first step to scaling the give dataset:
```{r echo=TRUE}
iris_data_scale <- scale(iris_data)
head(iris_data_scale,20)
```


For determine the value create visualization of scaling datasets with sumsquares
```{r eval=TRUE}
library(ggplot2)
library(factoextra)
```

**fviz_nbclust():** Dertemines and visualize the optimal number of clusters using different methods: within cluster sums of squares, average silhouette and gap statistics.
**"wss":** for total within sum of square
```{r echo=TRUE}
fviz_nbclust(iris_data_scale, kmeans, method = "wss") + 
  labs(title = "The elbow method")

```

The optimum cluster or value of k is where the elbow occur.

From the above graph we clearly see the elbow occur is on the point of 3.

So, the value of **k** is **3**.

### K-Means Model:
```{r echo=TRUE}
kmeans.model <- kmeans(iris_data, 3)
kmeans.model
```

After this code I can see size of these clusters, which means exact count of variables for cluster, in this case: 50, 62, 38.

For further information about accuracy of each species in cluster, I used:
```{r echo=TRUE}
table(iris$Species,kmeans.model$cluster)
```

## Visualization

Now visualization the cluster:
```{r echo=TRUE}
colnames(iris_data)
plot(iris_data[c("Sepal.Length","Sepal.Width")], 
     col = kmeans.model$cluster
     , pch = 19)
```

And after assigning centers we cans see that some of the dots are closer to one point than the other.

So, for that we create the cluster value visualization.

```{r eval=TRUE}
library(cluster)
library(fpc)
```

```{r echo=TRUE}
plotcluster(iris_data,kmeans.model$cluster)
```

```{r echo=TRUE}
clusplot(iris_data, kmeans.model$cluster, color = TRUE , shade = TRUE)
```

# Thank You!